### 2013-06-12 context-dependence.tex
.

@@

@@

>>>>

Here's a short example sequence with $\lambda=1$:
\begin{center}
 \setlength{\tabcolsep}{0pt}
\begin{tabular}{cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc}
X&X&X&O&O&X&O&O&O&O&X&O&X&O&X&X&O&O&X&O&O&X&O&X&X&X&O&X&O&O&O&X&X&O&X&O&O&O&X&X&O&O&O&X&O&O&O&O&X&O&X&X&O&X&X&O&O&X&O&O \\
$\centerdot$&O&X&O&X&O&O&O&X&$\centerdot$&O&X&O&O&X&X&X&o&x&$\centerdot$&o&O&X&x&x&O&X&O&X&o&o&O&X&X&$\centerdot$&$\centerdot$&o&o&O&X&X&o&$\centerdot$&O&X&$\centerdot$&o&o&$\centerdot$&$\centerdot$&O&X&X&x&O&X&o&O&X&$\centerdot$
\end{tabular}
\end{center}
here particles are X's, moving to the right; and spaces are O's; 
in the second line, 
$\centerdot$ is a position that has not considered a change; lowercase letters are positions that considered a change but did not;
and upper case are positions that did change.

@@

Here is an example, with all parameters equal to 1, for $t=.5$:
\begin{center}
 \setlength{\tabcolsep}{0pt}
\begin{tabular}{cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc}
X&X&O&X&X&O&O&X&O&X&O&X&X&O&O&X&O&O&O&O&X&X&X&O&X&O&X&O&X&O&O&O&X&X&O&X&X&X&X&X&O&X&O&X&O&X&X&X&X&O&O&X&X&X&X&X&X&O&O&O \\
x&x&o&x&X&X&O&x&o&x&$\centerdot$&x&x&O&X&X&$\centerdot$&O&X&O&X&x&x&o&x&o&x&o&x&O&X&O&$\centerdot$&$\centerdot$&O&O&X&X&O&X&X&X&o&x&o&$\centerdot$&X&O&X&o&o&x&X&X&X&O&X&o&$\centerdot$&$\centerdot$ 
\end{tabular}
\end{center}
The notation is as above; except that the entire matched pattern involved in a change is uppercase:
to simulate, we look in windows of size 3; so if XOO changes to XXO, the whole thing is uppercase, not just the middle X.

@@

Here is a short example, with all parameters equal to 1, with each branch of the tree having length $0.1$:
\begin{center}
 \setlength{\tabcolsep}{0pt}
\begin{tabular}{cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc}
T&G&G&A&G&A&G&G&T&C&T&G&C&C&A&T&A&G&A&C&G&G&G&C&G&C&C&G&C&C&T&A&G&G&A&G&C&C&G&C&G&T&T&T&T&G&C&G&T&G&G&T&G&T&T&G&T&G&G&C \\
$\centerdot$&$\centerdot$&g&C&G&a&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&T&A&C&A&$\centerdot$&$\centerdot$&$\centerdot$&T&A&T&$\centerdot$&$\centerdot$&$\centerdot$&T&G&c&C&C&A&C&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&G&G&G&t&A&T&$\centerdot$&$\centerdot$&G&A&g&C&G&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&t&T&G&A \\
$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&A&T&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&T&T&G&T&$\centerdot$&$\centerdot$&G&A&T&$\centerdot$&$\centerdot$&$\centerdot$&G&G&c&t&A&A&G&C&$\centerdot$&$\centerdot$&$\centerdot$&G&T&G&A&t&t&t&g&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&G&A&$\centerdot$&$\centerdot$&$\centerdot$&$\centerdot$&A&C 
\end{tabular}
\end{center}
Top is ancestral sequence (``unobserved''); bottom two are at the tips.
